\documentclass{muratcan_cv}

\setname{Alexandre Lachance}{}
\setaddress{Quebec City, Quebec, Canada}
\setmobile{+1 514-550-6196}
\setmail{alexandrelachance@me.com}
\setthemecolor{Black}
\setlinkedinaccount{https://www.linkedin.com/in/alexandre-lachance-36b497164/} 
\setgithubaccount{https://github.com/AlexandreLachanceGit} 


    
\begin{document}

%Create header
\headerview
\vspace{1ex} % white space
%
\section{Education}
\datedexperience{Master of Applied Science (M.A.Sc.) in Software Engineering}{Jan 2023 – Present}
\explanation{McMaster University | Expected Graduation: October 2024 | GPA: 3.98/4.00}{Hamilton, ON}
\datedexperience{Honours B.A.Sc. in Computer Science and Software Engineering}{Sep 2020 – Dec 2022}
\explanation{University of Quebec in Montreal | GPA: 3.90/4.30}{Montreal, QC}
\datedexperience{Diploma of College Studies (DCS) in Computer Science and Mathematics}{Sep 2018 – May 2020}
\explanation{Lionel-Groulx College}{Sainte-Thérèse, QC}

\section{Skills \& Interests}
\smallskip
\newcommand{\skillone}{\createskill{Programming Languages}{Rust \cpshalf Python \cpshalf Java \cpshalf C \cpshalf TypeScript \cpshalf C\#}}
%
\newcommand{\skilltwo}{\createskill{Technologies}{Linux \cpshalf Git \cpshalf GitHub CI/CD \cpshalf Docker \cpshalf AWS \cpshalf MPS \cpshalf Langium}}
%
\newcommand{\skillthree}{\createskill{Interests}{Software Architecture \cpshalf Programming Languages \cpshalf Generative Programming}}
%
\newcommand{\skillfour}{\createskill{Spoken Languages}{French \cpshalf English}}
%
\createskills{\skillfour, \skillone, \skilltwo, \skillthree}
\vspace{-3mm} % reduces whitespace!

\section{Experience \& Projects}
\datedexperience{Master's Thesis | Development of Lever: A Framework for DSL Editor Support}{Jan 2023 – Present}
\explanation{McMaster University | Supervised by \href{https://mosser.github.io/}{Sébastien Mosser}}{Hamilton, ON}
\explanationdetail{
	\smallskip
	\coloredbullet\ %
	Developed a lightweight framework used to create editor support for Domain-Specific Languages (DSLs).

	\smallskip
	\coloredbullet\ %
	Designed the framework to automatically generate both a Language Server and a VS Code extension.

	\smallskip
	\coloredbullet\ %
	Utilized Rust and leveraged its code generation capabilities for efficient development.

	\smallskip
	\coloredbullet\ %
	Developed editor support for P4, the standard language for programming Software-Defined Networks (SDNs).

	\smallskip
	\coloredbullet\ %
	Wrote the Tree-sitter (a parsing library) grammar for P4 and contributed it to the open-source Tree-sitter project.

	\smallskip
	\coloredbullet\ %
	Built languages using the Langium and MPS language workbenches.

	\smallskip
	\coloredbullet\ %
	Collaborated with industry partners (Intel, Telus) to improve and validate P4 support implementation.
}
%
\datedexperience{Teaching Assistant | Programming \& Software Design}{May 2023 – Jun 2024}
\explanation{McMaster University}{Hamilton, ON}
\explanationdetail{
	\smallskip
	\coloredbullet\ %
	Helped students grasp key programming concepts like recursion, control flow, and file handling.

	\smallskip
	\coloredbullet\ %
	Assisted with software design fundamentals, including design patterns and requirements.

	\smallskip
	\coloredbullet\ %
	Conducted labs, marked assignments, and provided one-on-one support during office hours.
}
%
\datedexperience{Research Assistant | Full-Stack Research Platform Development}{Jan 2022 – Jan 2023}
\explanation{University of Quebec in Montreal | Supervised by \href{https://mosser.github.io/}{Sébastien Mosser}}{Montreal, QC}
\explanationdetail{
	\smallskip
	\coloredbullet\ %
	Built a containerized web app for researchers to collect and analyze large datasets of Tweets.

	\smallskip
	\coloredbullet\ %
	Developed front-end (Angular, TypeScript) and back-end (Flask, Python).

	\smallskip
	\coloredbullet\ %
	Enabled comparison of datasets to identify behavioural patterns around specific topics.

	\smallskip
	\coloredbullet\ %
	Collaborated with communication professors to refine and adapt the platform to their needs.
}
%
\datedexperience{Research Intern | AI for Automatic Text Simplification}{Jun 2022 – Aug 2022}
\explanation{University of Quebec in Montreal | Supervised by \href{https://professeurs.uqam.ca/professeur/meurs.marie-jean/}{Marie-Jean Meurs}}{Montreal, QC}
\explanationdetail{
	\smallskip
	\coloredbullet\ %
	Researched AI-based solutions for text simplification by exploring the state of the art.

	\smallskip
	\coloredbullet\ %
	Gained proficiency in Natural Language Processing (NLP) and Machine Learning (ML) techniques.

	\smallskip
	\coloredbullet\ %
	Tested, debugged, and evaluated existing text simplification models.

	\smallskip
	\coloredbullet\ %
	Collaborated closely with Radio-Canada / CBC on practical applications of text simplification.
}
%
\datedexperience{Program Instructor / Tutor}{Jan 2022 – Apr 2022}
\explanation{University of Quebec in Montreal}{Montreal, QC}
\explanationdetail{
	\smallskip
	\coloredbullet\ %
	Assisted undergraduate students with course material, homework and other projects.

	\smallskip
	\coloredbullet\ %
	Coordinated with teacher assistants to help students in difficulty.
	\smallskip
}
%
\datedexperience{DCS Final Project | Virtual Reality Game}{Sep 2020 – Dec 2020}
\explanation{Lionel-Groulx College}{Sainte-Thérèse, QC}
\explanationdetail{
	\smallskip
	\coloredbullet\ %
	Built a Virtual Reality game in Unity (C\#), focusing on immersive gameplay and interaction.

	\smallskip
	\coloredbullet\ %
	Implemented procedurally generated maps and combat physics.
}
\pagebreak
%
\section{Publications}
%
\publication{Building Deduplicated Model Repositories to Assess Domain-Specific Languages Evolution}{Sep 2024}{\underline{Alexandre Lachance}, Sébastien Mosser}{\href{https://doi.org/10.1145/3652620.3688338}{10.1145/3652620.3688338}}
\explanationdetail{
	\smallskip
	\coloredbullet\ %
	Developed a deduplication framework for model repositories to support DSL evolution analysis.

	\smallskip
	\coloredbullet\ %
	Applied repository mining techniques to build a dataset and identify duplicates across multiple forges.

	\smallskip
	\coloredbullet\ %
	Validated the framework by testing the compatibility of DSL tools with evolving models.

	\smallskip
	\coloredbullet\ %
	Demonstrated the approach's effectiveness in reducing computational complexity for deduplication.
}
%
\publication{Automatic Text Simplification of News Articles in the Context of Public Broadcasting}{Dec 2022}{Diego Maupomé, Fanny Rancourt, Thomas Soulas, \underline{Alexandre Lachance}, \emph{et al.}}{\href{https://arxiv.org/abs/2212.13317}{10.48550/arXiv.2212.13317}}
\explanationdetail{
	\smallskip
	\coloredbullet\ %
	Explored automatic text simplification to improve accessibility for CBC/Radio-Canada news articles.

	\smallskip
	\coloredbullet\ %
	Compared modular lexical systems with end-to-end deep learning methods for simplification.

	\smallskip
	\coloredbullet\ %
	Evaluated automatic text simplification using both manual and automatic methods to assess performance.

	\smallskip
	\coloredbullet\ %
	Achieved promising results with paraphrase-based models on sentence simplification tasks.
}
\vspace{0.5em}
%
\section{Presentations}
%
\datedexperience{Building Deduplicated Model Repositories to Assess Domain-Specific Languages Evolution}{Sep 2024}
\explanation{Models and Evolution Workshop, Models 2024}{Linz, Austria}
%
\datedexperience{From Zero to VS Code: A Framework Approach to Language Support}{Nov 2023}
\explanation{MDENet Research Demonstration | Link to video: \scriptsize \url{https://www.youtube.com/watch?v=JzCYxz4G_Cc}}{Online}
%
\datedexperience{Developing a Modular Language Server to Support P4 Developers}{Sep 2023}
\explanation{P4 Developers Days Meeting}{Online}
%
\datedexperience{A Language Engineering Approach to Support the P4 Coding Ecosystem}{Apr 2023}
\explanation{P4 Workshop at Intel HQ | Link to publication: \scriptsize \url{https://macsphere.mcmaster.ca/handle/11375/28616}}{San Francisco, USA}
%
\section{Extracurricular Activities}
\datedexperience{Executive Secretary | Students Association}{Jun 2022 – Dec 2022}
\explanation{AGEEI (General Association of Computer Science Students) at University of Quebec in Montreal}{Montreal, QC}
\explanationdetail{
	\smallskip
	\coloredbullet\ %
	Attended executive and general meetings, drafting minutes.

	\smallskip
	\coloredbullet\ %
	Handled official correspondence and archived legal/administrative documents.

	\smallskip
	\coloredbullet\ %
	Ensured adherence to General Assembly decisions.

	\smallskip
	\coloredbullet\ %
	Managed an online community of 1200+ students, addressing course-related inquiries.
}
\datedexperience{Cybersecurity Competition Team Member}{Sep 2021 – Dec 2022}
\explanation{University of Quebec in Montreal}{Montreal, QC}
\explanationdetail{
	\smallskip
	\coloredbullet\ %
	Participated in "Capture The Flag" events such as Hackfest 2021, NorthSec 2022, and Hackfest 2022.

	\smallskip
	\coloredbullet\ %
	Collaborated with peers to solve cybersecurity challenges and improve cybersecurity knowledge.
}

% 
\smallskip

\section{Other Achievements}
\indent
\explanationdetail{
	\smallskip
	\coloredbullet\ %
	\textbf{Scholarship of Excellence} granted by the government of Quebec in 2021.
}
\end{document}
